Exploring Design Space for Differentially Private Bayesian Inference

### 2019-01-05 ICML2019/main.tex
adjust the format

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying Hellinger distance in our case, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
when $t \geq 0$, and\\
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
\end{array}
$$
when $t < 0$.\\

% When $\alpha = \beta$, we also have:
% \begin{align*}
%  Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
% \leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
%   = \quad & Pr[ - t \leq Y < t + 1] \\
%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
%  \end{align*}
Unfolding the Hellinger distance formula, we get:\\
  \noindent \textbf{case: t is even}\\
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 \\
  & = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

%   We also have:
%   \begin{align*}
%   & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
%   \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
%   \cdot
%   \prod_{k = 1}^{\frac{t}{2}}
%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}}),
%   \end{align*} 
%   when $\alpha = \beta$.
% in 2 dimensions, where $\epsilon = 1.0$. 
% \begin{itemize}
% 	\item \textbf{Case} of baseline Laplace mechanism, where $\Delta \bysinfer = 2$:\\

% 	\item \textbf{Case} of improved Laplace mechanism, where $\Delta \bysinfer = 1$
% \end{itemize}

@@

Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:

  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.

  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.

  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.

@@

\subsection{Accuracy Comparison between $\hexpmech$, $\lapmech$ and $\ilapmech$}
For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.
\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
    \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
 & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.11932560927 & 0.07237464051 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.11627207896 & 0.04277410743 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ 
 & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
 \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
 & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

@@

By solving following equations:
\begin{itemize}
  \item
\[
\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer.

  \item 
\[
\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
 = 0.119325609\ or\ 0.116272079
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
\vspace{12cm}
  \item 
\[
\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
     = 0.072374641\ or\ 0.042774107
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one.

  \item Following equations can be in the same way.
\end{itemize}

%   Unfolding the Hellinegr distance in this accuracy formula:
%  \begin{itemize}

%   \item[\textbf{case 1:}] \textbf{t is even}

%   \begin{align*}
%   &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z)^2 = 
%   1 - \prod_{k = 0}^{\frac{t}{2} - 1}
%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
%   \cdot
%   \prod_{k = 1}^{\frac{t}{2}}
%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ }\\
%   = & \frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \prod_{k = 0}^{\frac{t}{2} - 1}
%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
%   \cdot
%   \prod_{k = 1}^{\frac{t}{2}}
%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}}}{4 S(\dataobs)})}}
%   {\nomalizer{\dataobs}}
%   \end{align*}

%   \item[\textbf{case 2:}] \textbf{t is odd}

%   \begin{align*}
%   c^2 = \qquad &
%   1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
%   \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
%   \qquad &\cdot 
%   \prod_{k = 0}^{m-1}
%   \sqrt{(1 + \frac{1}{2(\alpha + k)})
%   (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
%   } \\
%   \qquad & \cdot 
%   \prod_{k = 1}^{m} 
%   \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}
%   \end{align*}
%   Substitute the $c$ in Equation, (\ref{eq_acc})

% \end{itemize}

>>>>

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying Hellinger distance in our case, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] \\
& =  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
when $t \geq 0$, and\\
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big]\\
& = \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}).
\end{array}
$$
when $t < 0$.\\
Unfolding the Hellinger distance formula, we get:\\
  \noindent \textbf{case: t is even}\\
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 \\
  & = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

@@

  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

\subsection{Accuracy Comparison between $\hexpmech$, $\lapmech$ and $\ilapmech$}
For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.
\begin{table*}[t]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
    \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
 & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.11932560927 & 0.07237464051 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.11627207896 & 0.04277410743 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table*}

In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
\begin{table*}[t]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ 
 & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
 \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
 & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table*}

@@

By solving following equations:
  \[
  \frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
  \[
  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
   = 0.119325609\ or\ 0.116272079
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
  \[
\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
     = 0.072374641\ or\ 0.042774107
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.
